MSB1015_Assignment 2

### 2019-10-13 MSB1015_Assignment2_SuzannetenHage.Rmd
Added package citations
Citations for all packages used, found using the citation() function in R.

>>>>

*Package references*
* WikidataQuerySerivceR
  Mikhail Popov (2017). WikidataQueryServiceR: API Client Library for
  'Wikidata Query Service'. R package version 0.1.1.
  https://CRAN.R-project.org/package=WikidataQueryServiceR

*rJava
  Simon Urbanek (2019). rJava: Low-Level R to Java Interface. R package
  version 0.9-11. https://CRAN.R-project.org/package=rJava

*rcdk
  Guha, R. (2007). 'Chemical Informatics Functionality in R'. Journal
  of Statistical Software 6(18)

*stringi
  Gagolewski M. and others (2019). R package stringi: Character string
  processing facilities. http://www.gagolewski.com/software/stringi/.

*caTools
  Jarek Tuszynski (2019). caTools: Tools: moving window statistics,
  GIF, Base64, ROC AUC, etc.. R package version 1.17.1.2.
  https://CRAN.R-project.org/package=caTools

*pls
  Bjørn-Helge Mevik, Ron Wehrens and Kristian Hovde Liland (2019). pls:
  Partial Least Squares and Principal Component Regression. R package
  version 2.7-1. https://CRAN.R-project.org/package=pls

*Metrics
  Ben Hamner and Michael Frasco (2018). Metrics: Evaluation Metrics for
  Machine Learning. R package version 0.1.4.
  https://CRAN.R-project.org/package=Metrics
